Machine Learning, a Review for Tree Segmentations Task

### 2024-04-04 Notebook LaTEX/Machine Learning/main.tex
>w< mcbr

\title{Machine Learning, a Review for Tree Segmentations Task}
\author{Hongda Li}

@@

\begin{abstract}
    This is my own notes. 
\end{abstract}

@@

            \item \inlinecode{bias}: Add learnable bias to the component, default to `true`. 
        \end{enumerate}

@@

\section{Graphical Model and Probability Dependence}

@@

>>>>

\title{Machine Learning, a Review for Tree Segmentations Task}
\author{}

@@

\begin{abstract}
    This is my own notes. 
\end{abstract}
\tableofcontents

@@

            \item \inlinecode{bias}: Add learnable bias to the component, default to `true'. 
        \end{enumerate}

@@

\section{Graphical Model and Probability Dependence}
    Graphical models are used to model probability dependence between random variables. 
    In the context of deep learning, it helps with training hierarchical models.

@@

\section{Case Study | Forest Allometrics Extractions, Predictions}
